\section{Technologies}
\label{sec:technologies}
Germinate uses third-party software libraries to extend its functionality. The following sections will list these libraries and explain their purpose:

\subsection{JavaScript libraries}

\begin{description}[align=left,style=nextline,leftmargin=*,labelsep=\parindent,font=\bfseries]
	\item[CookieCuttr] Because of the EU "Cookie Law", websites have to let the user know when they're using cookies. CookieCuttr displays a banner notifying the user of just that.\\\url{https://github.com/weare2ndfloor/cookieCuttr}
	\item[D3.js] We us D3.js to generate dynamic and interactive data visualizations. Almost all charts in Germinate are created using this library.\\\url{https://github.com/mbostock/d3}
	\item[d3Pie] This is a plugin for D3.js that we use to easily create pie charts.\\\url{https://github.com/benkeen/d3pie}
	\item[D3.tip] This is a plugin for D3.js that allows easy creation of tooltips for SVG elements.\\\url{https://github.com/Caged/d3-tip}
	\item[FancyBox] FancyBox is used to create popups of images and text. \\\url{https://github.com/fancyapps/fancyBox}
	\item[html2canvas] html2canvas is used to convert the d3.js chart legend to an image and download it.
	\\\url{https://github.com/niklasvh/html2canvas}
	\item[jQuery] jQuery is the most popular JavaScript library out there. It allows easy selection, traversal and manipulation of DOM elements. \\\url{https://github.com/jquery/jquery}
	\item[jQuery.freezeheader] We use a highly customized version of this library to make our table headers "freeze", i.e. when you scroll down the page, the table header will stick to the top of the window once you scroll past it. \\\url{https://github.com/laertejjunior/freezeheader}
	\item[lasso.js]  This is a plugin for D3.js that allows freehand drawing of selections within D3.js charts.\\\url{https://github.com/skokenes/D3-Lasso-Plugin}
	\item[MarkerClustererPlus] We us this library to group large numbers of markers on a Google Maps into a smaller number of clusters. This emphasizes regions with many markers without cluttering the map with individual pins.\\\url{https://github.com/googlemaps/js-marker-clusterer}
	\item[OverlappingMarkerSpiderfier] This spiderfier is used to allow easy selection of pins on a Google Map with a high density of markers. When clicked, the pins will be spread out so that the user can then select the marker of interest.\\\url{https://github.com/jawj/OverlappingMarkerSpiderfier}
	\item[prettify.js] Prettify is used to make code on website more pretty, e.g. it adds basic syntax highlighting. The main use of this library is for the SQL debug messages that appear when Germinate is run in debug mode.\\\url{https://github.com/google/code-prettify}
	\item[saveSvgAsPng.js] This library allows the user to save a SVG image in the browser (usually generated by D3.js) to a PNG file on their computer.\\\url{https://github.com/exupero/saveSvgAsPng}
	\item[Spectrum] Spectrum allows us to easily add color-pickers to the web-interface. HTML5 introduced the color-type input element, but many current browsers still don't support it. We also always have to consider users with outdated browsers, so unfortunately we have to fall back to a third-party library for this purpose.\\\url{https://github.com/bgrins/spectrum}
	\item[toastr] Toastr is a library that allows us to show notifications similar to Gnome / Growl notifications on the desktop. \\\url{https://github.com/CodeSeven/toastr}
\end{description}

\subsection{Font frameworks}

\begin{description}[align=left,style=nextline,leftmargin=*,labelsep=\parindent,font=\bfseries]
	\item[Font Awesome] This is a truly awesome framework containing loads of pictographic icons that we use throughout Germinate. They are fully scalable which makes them a perfect replacement for raster images. \\\url{https://github.com/FortAwesome/Font-Awesome}
\end{description}

\subsection{Java libraries}
\begin{description}[align=left,style=nextline,leftmargin=*,labelsep=\parindent,font=\bfseries]
	\item[Apache Commons FileUpload] This library is used to make the upload of files from the browser to the server easier. \\\url{https://github.com/apache/commons-fileupload}
	\item[Apache Commons IO] This is a widely used utility library. \\\url{https://github.com/apache/commons-io}
	\item[Apache Commons Logging] A popular logging library. \\\url{https://github.com/apache/commons-logging}
	\item[Apache HttpComponents Client] This library is used to easily communicate with Gatekeeper via HTTP requests. \\\url{https://github.com/apache/httpclient}
	\item[Apache HttpComponents Core] Required by Apache HttpComponents Client. \\\url{https://github.com/apache/httpcore}
	\item[Flapjack] Flapjack is a graphical genotype viewer developed at The James Hutton Institute. Germinate uses it on the server side to export genotypic data and allele frequency data. \\\url{https://ics.hutton.ac.uk/flapjack}
	\item[Flyway] Flyway is a database migration tool that Germinate uses to update its database between releases.
	\\\url{https://flywaydb.org}
	\item[GWT] GWT is the main building stone of Germinate. It's the web development framework we chose to use. \\\url{https://github.com/gwtproject/gwt}
	\item[GWT-Charts] This is a GWT implementation of the JavaScript Google Charts API. \\\url{https://code.google.com/p/gwt-charts}
	\item[GWT-Maps-V3-Api] This is a GWT implementation of the JavaScript Google Maps API. \\\url{https://github.com/branflake2267/GWT-Maps-V3-Api}
	\item[GwtQuery] We use this library to use jQuery-like code in Java. \\\url{https://github.com/ArcBees/gwtquery}
	\item[GWT-Tour] This is a GWT API for the hopscotch framework. It's used to generate "tours" for users, i.e. step-by-step instructions for using the web-interface. \\\url{https://github.com/eemi2010/gwt-tour}
	\item[jBCrypt] jBCrypt is a Java implementation of the OpenBSD's Blowfish password hashing algorithm. \\\url{https://github.com/jeremyh/jBCrypt}
	\item[JAK] This "Java API for KML" is used when exporting geographic information to KML format. \\\url{https://github.com/micromata/javaapiforkml}
	\item[JAXB] Required by JAK.\\\url{https://jaxb.java.net/}
	\item[MySQL Connector/J] This is a library that allows us to easily communicate with a MySQL database from Java code. \\\url{https://github.com/mysql/mysql-connector-j}
	\item[Thumbnailator] This is a utility library used to create thumbnails of images. Whenever a new image is copied to the full-size image folder of Germinate, we will use this library to automatically generate a thumbnail for it. \\\url{https://github.com/coobird/thumbnailator}
\end{description}